Interpretable Machine Learning

### 2019-01-15 chunks/story-wines.Rmd
fixes plot
adds intuition for counterfactual explanations

```{r}
shap = Shapley$new(pred, x.interest = worst)
plot(shap) + 
  scale_y_discrete("") + 
  scale_x_continuous("Feature contribution")
```

## What needs to change?

TODO: Slide to explain counterfactuals

>>>>

```{r}
shap = Shapley$new(pred, x.interest = worst)
plot(shap) + 
  scale_x_discrete("") + 
  scale_y_continuous("Feature contribution")
```

## Counterfactual Explanations  {.center data-background=../images/counterfactual-intuition-1.png data-background-size=contain}

## Counterfactual Explanations  {.center data-background=../images/counterfactual-intuition-2.png data-background-size=contain}

## Counterfactual Explanations  {.center data-background=../images/counterfactual-intuition-3.png data-background-size=contain}
